---
title: "615 Assignment 4 Task 3"
author: "Boyu Chen"
date: "12/6/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidytext)
library(textdata)
library(tidyverse)
library(gutenbergr)
library(scales)
library(ggplot2)
library(tidyr)
library(dplyr)
library(wordcloud)
library(reshape2)
library(magrittr)
library(sentimentr)
library(tnum)
tnum.authorize("mssp1.bu.edu")
tnum.setSpace("test2")
```

```{r}
 # Get the function from source
source("Book2TN-v6A-1.R")             
book<-gutenberg_download(105)
# output book into txt file. 
# write.table(book,"book.txt")      
newbook <- book %>%
  mutate(
    linenumber = row_number(),
    chapter = cumsum(str_detect(text, 
                                regex("^chapter [\\divxlc]", 
                                      ignore_case = TRUE)))) %>% 
  unnest_tokens(word, text) 


 # rename the book into tidy_book
tidy_books <- book                    
 # read txt table
book_fix <- read.table("book.txt", header = T)    
 # Upload book to server
# tnBooksFromLines(book_fix$text, "Jane_Austen/persuation")  
# query from tnum server
TQ5<- tnum.query('Jane_Austen/persuation/section# has text',max=70000)  
# get the tnum method of words
DF5 <- tnum.objectsToDf(TQ5)
# get the table for book
DF5 %>% select(subject:numeric.value)%>% head()  
 # Select sentence from book in subject,section,value method.
book_sentence<-DF5 %>% separate(col=subject, 
                  into = c("path1", "path2","section",
                           "paragraph","sentence"), 
                  sep = "/", 
                  fill = "right") %>% 
  select(section:string.value)
book_sentence<-book_sentence %>% 
  mutate_at(c('section','paragraph','sentence'),~str_extract_all(.,"\\d+") %>% 
              unlist() %>% as.numeric())


```



Compare with Task2
```{r}
# I use sentimentr to get sentiment score group by thee 
# scores with each section to get the average result
sentence_out <- book_sentence %>%
  dplyr::mutate(sentence_split = get_sentences(string.value)) %$%
    sentiment_by(sentence_split, list(section))
# And plot them
plot(sentence_out)
```


```{r}
# create a new bing with index=chapter
new_bing <- newbook %>% 
    inner_join(get_sentiments("bing")) %>%
    mutate(method = "Bing et al.") %>% 
    count(method, index = chapter, sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n,
              values_fill = 0) %>% 
  mutate(sentiment = positive - negative)


# Creat zscore function 
zscore<-function(input){
  return((input-min(input))/(max(input)-min(input)))
  
}
# get the zscore for sentence and word in bing dictionary 
new_bing2 <- new_bing %>% 
  mutate(bing_scale = zscore(sentiment)) %>% 
  select(method, index, bing_scale)

# Rename colname in order to join by section
colnames(new_bing2)[2]='section'
```

```{r, echo = TRUE}
# get the zscore for sentence_out
sentence_out <- sentence_out %>%
  mutate(sentimentr_scale = zscore(ave_sentiment))

# join two data frame together
sentence_out_2method <- left_join(sentence_out,new_bing2,by='section')%>%
  select(section,bing_scale,sentimentr_scale)

# use pivot longer for ggplot
sentence_out_2method_plot <- sentence_out_2method %>% 
  pivot_longer(cols = c('sentimentr_scale','bing_scale'), 
               names_to = 'sentiment')

# create barplot to compare
sentence_out_2method_plot %>% 
  ggplot(aes(y = value,x = factor(section))) +
  geom_bar(aes(fill = factor(sentiment)), 
           stat = 'identity', position = "dodge",width = 0.7) + 
  theme_bw()
```

The graph shows the difference between bing zscore and sentiment zscore. We can find that the trend are similar however, the difference between zscore is much larger.In some of the chapter, some words through bing dictionary are more optimistic than sentimentr. However, in some chapter some words through bing dictionary are pessimistic. I think sentiment is much better



Reference: https://www.gutenberg.org/ebooks/105
Code are reference from Yuli Jin. Github:https://github.com/MA615-Yuli/MA615_assignment4_new
and from https://www.tidytextmining.com/sentiment.html

Difference between my code and Jin's code is that due to my book have much more positive words than negative words, I use zscore instead of scale to compare. According to zscore, I can find the similar trend. Without zscore, I found the different trend for emotion for each section.


